Proportional multi-state multiple-cohort life table model

### 2018-10-11 code/MSLT/MSLTdoc.Rmd
Updating RMarkdown code

Once the selections described in Table 2 are made, the option *Download CVS** in the GHDx website is selected. A prompt comes up asking for an email address. The data is sent to the designated email address (within minutes) in ZIP format, unzip and use the code below to read the data (4). Here, we selected data for Greater London and England. The aim is to compare and derive scaling factors as for most cities the data is not available from the GBD and country level data may be used and scaled to the city level. Note that the data input requirement for the PMSLT, except population numbers, is in rates. Therefore the scaling is to better reflect the burden of an area, this is a different issue than working with numbers (e.g. total mortality numbers, total YLDs numbers) as in the ITHIM approach.

4) Read GBD data
```{r chunk-4}
```

@@

5) Change all upper cases to lower case and delete () from variables.
```{r chunk-5}
```

6) Create age categories index in GBDdata (mid age, to match cohort running), total of 20 age groups. These are the age cohorts to simulate.
```{r chunk-6}
```

7) Create age and sex categories to obtain population numbers. Population numbers from GBD are used in Dismod II. For the Life table (Figure 3), the numbers may be from the synthetic population. For now, the Life table is set up with population numbers derived from the GBD data.
```{r chunk-7}
```

8) Convert string variables to numeric to do calculations.
```{r chunk-8}
```

9) Generate population numbers for Greater London in a new data frame ("GBD_population"). Note that there is data for England as well, which is used in a separate rmarkdown document (GBDCompare). Population numbers are derived from rates per 100,000 and total numbers of cases. 
```{r chunk-9}
```
10) Generate population numbers from given number of cases and rates per 100,000 people. 
```{r chunk-10}
```
11) Remove rows with zero
```{r chunk-11}
```

12) Keep relevant variables
```{r chunk-12}
```
13) Create data frames for Greater London to be later used for: a) interpolation of rates and b) PMLT cohorts. 
```{r chunk-13}
```

14) Check population total numbers
```{r chunk-14}
```

15) Generate data frames for Greater London with per person rates (per 100,000 in original data).  
```{r chunk-15}
```

>>>>

Once the selections described in Table 2 are made, the option *Download CVS** in the GHDx website is selected. A prompt comes up asking for an email address. The data is sent to the designated email address (within minutes) in ZIP format, unzip and use the code below to read the data (4). Here, we selected data for Greater London. The aim is to compare and derive scaling factors as for most cities the data is not available from the GBD and country level data may be used and scaled to the city level. Note that the data input requirement for the PMSLT, except population numbers, is in rates. Therefore the scaling is to better reflect the burden of an area, this is a different issue than working with numbers (e.g. total mortality numbers, total YLDs numbers) as in the ITHIM approach.

4) Generate Dismod input dataset
```{r chunk-4}
```

@@

5) Generate data for the proportional-multi state life table by single age-year (mslt_df).
```{r chunk-5}
```

6) Add Dismod output to mslt_df.
```{r chunk-6}
```

7) Generate baseline general life tables.
```{r chunk-7}
```

8) Generate baseline disease life table.
```{r chunk-8}
```

9) Factor to multiply by incidence, will be replaced by (1-PIF) and generate scenario incidence.
```{r chunk-9}
```
10) Generate scenario disease life tables. 
```{r chunk-10}
```
11) Generate all-cause mortality and all-cause years with disability rate for scenario and use in scenario general life table. 
```{r chunk-11}
```

12) Generate a list of disease outputs by age and sex.  
```{r chunk-12}
```
13)  Generate a general dataframe for all age-sex cohort disease specific outcomes.
```{r chunk-13}
```

14) Generate graphs for changes in burden of disease by age and sex (incidence and mortality)
```{r chunk-14}
```

15) Generate aggregated (all cohorts) outcomes by sex.

```{r chunk-15}
```
